*Symbiodinium* communities in reef corals of St. John, U.S.V.I. (2012)

### 2016-09-06 analysis/STJ2012_analysis.Rmd
import both blast and nw

```{r setup_2, include=FALSE}
# Load all R scripts in "R/" directory
sapply(list.files(path="R", pattern="*[^w].R", full.names=TRUE), source, .GlobalEnv)
# Load package libraries
library(phyloseq); library(vegan); library(multcompView); library(reshape2); library(igraph); library(stringr)
# Set colors for plotting clades
taxcolors <- matrix(c("#8dd3c7", "#ffffb3", "#bebada", "#fb8072", "#80b1d3", "#fdb462"), 
                    dimnames=list(c("CladeA", "CladeB", "CladeC", "CladeD", "CladeF", "CladeG")))
```

@@

# Data pre-processing
### Import dataset
The [phyloseq](https://joey711.github.io/phyloseq/) package is used here to combine the OTU table, taxonomic assignments, and sample metadata into a single R data object (class 'phyloseq') to facilitate downstream analyses.
```{r data_import, cache=T}

```{r filter_taxa}
# Import taxonomic assignment data from blast and nw
blast.res.colnames <- c("otu", "BLAST.hit", "pct.id", "B.length", "B.mismatches", "B.gapopen", 
                        "q.start", "q.end", "s.start", "s.end", "e.val", "bit.score")
tax.import <- function(b, nw) {
  m <- merge(read.table(b, col.names=blast.res.colnames, stringsAsFactors=FALSE),
             read.table(nw, stringsAsFactors=FALSE), by="otu")
  rownames(m) <- m$otu
  m$Clade <- str_extract(m$nw.hits, pattern="^.")
  return(m)
}

tax97 <- tax.import(b="data/otus_97/blast_tophits.txt", nw="data/otus_97/nw_tophits.tsv")
tax100 <- tax.import(b="data/otus_100/blast_tophits.txt", nw="data/otus_100/nw_tophits.tsv")
tax97bs <- tax.import(b="data/otus_97_bysample/blast_tophits.txt", nw="data/otus_97_bysample/nw_tophits.tsv")
tax97bsp <- tax.import(b="data/otus_97_byspecies/blast_tophits.txt", nw="data/otus_97_byspecies/nw_tophits.tsv")

@@

# Replace any sequence in taxonomy assignment that is a member of a group of identical sequences with the name of the group
collapse.idents <- function(df) {
  within(df, {
    for (i in 1:nrow(ident)) {
      BLAST.hit <- gsub(ident[i,1], ident[i,2], BLAST.hit)
      nw.hits <- gsub(ident[i,1], ident[i,2], nw.hits)
      nw.hit1 <- gsub(ident[i,1], ident[i,2], nw.hit1)
    }
  })
}

>>>>

```{r setup_2, include=FALSE}
# Load all R scripts in "R/" directory
source("R/functions.R", .GlobalEnv)
# Load package libraries
library(phyloseq); library(vegan); library(multcompView); library(reshape2); library(igraph); library(stringr)
# Set colors for plotting clades
taxcolors <- matrix(c("#8dd3c7", "#ffffb3", "#bebada", "#fb8072", "#80b1d3", "#fdb462"), 
                    dimnames=list(c("CladeA", "CladeB", "CladeC", "CladeD", "CladeF", "CladeG")))
```

@@

# Data pre-processing
### Import dataset
The [phyloseq](https://joey711.github.io/phyloseq/) package is used here to combine the OTU table, taxonomic assignments, and sample metadata into a single R data object (class 'phyloseq') to facilitate downstream analyses.
```{r import_taxa_data, cache=T}
# Import taxonomic assignment data from blast and nw

read.blast <- function(file) {
  b <- read.table(file, stringsAsFactors=FALSE,
                  col.names=c("otu", "pct.id", "length", "mismatches", "gapopen", "q.start", "q.end", 
                              "s.start", "s.end", "e.val", "bit.score", "hit"))
  b <- b[order(b$otu),]
  return(b)
}
b <- read.blast("data/otus_97/blast_tophits.tsv")

read.nw <- function(file) {
  nw <- read.table(file, stringsAsFactors=FALSE)
  nw <- nw[order(nw$otu),]
  return(nw)
}
nw <- read.nw("data/otus_97/nw_tophits.tsv")

tax.import <- function(bfp, nwfp) {
  b <- read.table(bfp, col.names=blast.res.colnames, stringsAsFactors=FALSE)
  b <- b[order(b$otu),]
  ag <- aggregate(data.frame(BLAST.hit=b$BLAST.hit), by=list(otu=b$otu), FUN=function(x) paste0(x, collapse=";"))
  b2 <- b[!duplicated(b$otu), ]
  b2$BLAST.hit <- ag$BLAST.hit
  nw <- read.table(nwfp, stringsAsFactors=FALSE)
  m <- merge(b2, nw, by="otu")
  rownames(m) <- m$otu
  m$Clade <- str_extract(m$nw.hits, pattern="^.")
  return(m)
}

tax97 <- tax.import(bfp="data/otus_97/blast_tophits_withties.txt", nwfp="data/otus_97/nw_tophits.tsv")
tax100 <- tax.import(bfp="data/otus_100/blast_tophits.txt", nwfp="data/otus_100/nw_tophits.tsv")
tax97bs <- tax.import(bfp="data/otus_97_bysample/blast_tophits.txt", nwfp="data/otus_97_bysample/nw_tophits.tsv")
tax97bsp <- tax.import(bfp="data/otus_97_byspecies/blast_tophits.txt", nwfp="data/otus_97_byspecies/nw_tophits.tsv")

@@

# Replace any sequence name in taxonomy assignment that is a member of a group of identical sequences with the name of the group
collapse.idents <- function(df) {
  within(df, {
    for (i in 1:nrow(ident)) {
      BLAST.hit <- gsub(ident[i,1], ident[i,2], BLAST.hit)
      nw.hits <- gsub(ident[i,1], ident[i,2], nw.hits)
      nw.hit1 <- gsub(ident[i,1], ident[i,2], nw.hit1)
    }
  })
}
